Minimax-optimal Laplacian Eigenmaps regression over Sobolev Spaces with Neighborhood Graphs

### 2021-03-29 manuscripts/laplacian_eigenmaps/appendix.tex
Finished editting higher-order section of Laplacian eigenmaps paper.
Added organization for laplacian eigenmaps proofs.

\begin{lemma}
	Suppose we observe $(Y_1,x_1),\ldots,(Y_n,x_n)$ according to~\eqref{eqn:fixed_graph_regression_model}.
	\begin{itemize}
		\item If $f_0 = 0$, then $\Ebb_0[\varphi] \leq a$.
		\item Suppose $f_0 \neq 0$ satisfies
		\begin{equation*}
		\sum_{k = 1}^{K} \dotp{f_0}{v_k}_n^2 \geq 16\frac{\sqrt{2K}}{n}\biggl(\sqrt{\frac{1}{a}} + \frac{1}{b}\biggr).
		\end{equation*}
		Then $\Ebb_{f_0}[1 - \phi] \leq b$.
	\end{itemize}
\end{lemma}

\section{Proofs in Manifold Setting}
\label{sec:manifold_proofs}

@@

\section{Comparison of Laplacian eigenmaps and kernel smoothing in non-uniform density setting}

@@

>>>>

\begin{lemma}
	Suppose we observe $(Y_1,x_1),\ldots,(Y_n,x_n)$ according to~\eqref{eqn:fixed_graph_regression_model}.
	\begin{itemize}
		\item If $f_0 = 0$, then $\Ebb_0[\varphi] \leq a$.
		\item Suppose $f_0 \neq 0$ satisfies
		\begin{equation*}
		\sum_{k = 1}^{K} \dotp{f_0}{v_k}_n^2 \geq 16\frac{\sqrt{2K}}{n}\biggl[\sqrt{\frac{1}{a}} + \frac{1}{b}\biggr].
		\end{equation*}
		Then $\Ebb_{f_0}[1 - \phi] \leq b$.
	\end{itemize}
\end{lemma}

\section{Graph quadratic form, flat Euclidean domain}
\label{sec:graph_quadratic_form_euclidean}

\section{Graph quadratic form, manifold domain}
\label{sec:graph_quadratic_form_manifold}

@@

\section{Lower bound on empirical norm}
\label{sec:empirical_norm}
In this Section we prove Proposition~\ref{prop:empirical_norm_sobolev} (in Section~\ref{subsec:empirical_norm_sobolev}). We also prove an analogous result when $\mc{X}$ is a manifold as in Model~\ref{def:model_manifold} (in Section~\ref{subsec:empirical_norm_sobolev_manifold}), and we prove some sharper estimates in the case where the function is bounded in H\"{o}lder norm, in Section~\ref{subsec:empirical_norm_holder}.

\subsection{Proof of Proposition~\ref{prop:empirical_norm_sobolev}}
\label{subsec:empirical_norm_sobolev}
\textcolor{red}{(TODO)}

\subsection{Analysis of empirical norm in manifold setting}
\label{subsec:empirical_norm_soboolev_manifold}

\subsection{Better bounds assuming H\"{o}lder smoothness}
\label{subsec:empirical_norm_holder}

\section{Analysis of kernel smoothing}
\label{subsec:kernel_smoothing}
In this section we prove Lemma~\ref{lem:kernel_smoothing_laplacian_eigenmaps} (in Section~\ref{subsec:pf_kernel_smoothing_laplacian_eigenmaps}) and Lemma~\ref{lem:kernel_smoothing_bias} (in Section~\ref{subsec:pf_kernel_smoothing_bias}). In Section~\ref{subsec:eigenmaps_beats_kernel_smoothing}, we give a sequence $\{p^{(n)}(x), f_0^{(n)}(x)\}_{n \in \mathbb{N}}$ for which the estimator $T_{h,n}\wc{f}$ (kernel extension of Laplacian eigenmaps) dominates direct kernel smoothing of the responses, in the sense that
\begin{equation*}
\lim_{n \to \infty} \sup_{h'} \frac{\|T_{h_n,n}\wc{f} - f_0\|_P^2}{\|T_{h',n}Y - f_0\|_P^2 } = 0,\quad \textrm{with probability $1$.}
\end{equation*}

\subsection{Proof of Lemma~\ref{lem:kernel_smoothing_laplacian_eigenmaps}}
\label{subsec:pf_kernel_smoothing_laplacian_eigenmaps}

\subsection{Proof of Lemma~\ref{lem:kernel_smoothing_bias}}
\label{subsec:pf_kernel_smoothing_bias}

\subsection{Comparison of Laplacian eigenmaps to kernel smoothing}
\label{subsec:eigenmaps_beats_kernel_smoothing}

@@

\section{Miscellaneous}
Here we give some helpful Lemmas used at various points in the above proofs. We also prove that spectral sparsification does not change the rate of convergence of $\wh{f}$.
